Tidy data structure to support exploration and modeling of temporal data

### 2019-01-08 main.Rmd
added count-gaps plot

>>>>

During a power outage, electricity usage for some households may become unavailable, thus resulting in implicit missing values in the database. Gaps in time occur to `r scales::percent(sum(gap_df$.gaps) / NROW(gap_df))` of the households in this dataset. It would be interesting to explore these missing patterns as part of preliminary analysis. Since the smart meter has been installed at different dates for each household, it is reasonable to assume that the records are obtainable for different time lengths for the households, instead of full lengths across the households. Figure \@ref(fig:count-gaps) reveals the gaps for the top 49 households and the rest collapsed into a single batch arranged in rows from high to low in tallies. Missing values can be found at any time point during the entire time span. A small number of customers have undergone energy unavailability in consecutive hours, indicated by a line range in the plot. On the other hand, the majority suffer occasional breakdown with more frequent happenings in January.

(ref:count-gaps-cap) Time gap plots for the top 49 customers with most implicit missing values and the rest grouped into the one. Each cross represents the missing in time and a line between two dots shows continuous missingness over time. Each row corresponds to one customer describes the incidences of time gaps.
